### 2019-02-21 appendices/proofs.tex
remove superfluous newlines in proofs

\begin{proof}
  We prove Theorem~\ref{thm:pres-eval} by induction on $e$:\\

@@

\begin{proof}
  We prove Lemma~\ref{lem:presvalue} by induction over $e$.\\

@@

  % \noindent\textbf{Case} $\Value{(u\At t,s)}=\Value(t,s)$ This case follows
  % directly from the induction hypothesis.\\
\end{proof}

@@

\begin{proof}
  We prove Theorem~\ref{thm:pres-stride} by induction on $e$:\\

@@

  \case{$\userule{S-ThenCont}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By Lemma~\ref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By Theorem~\ref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.}
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.\\

@@

\begin{proof}
  We prove Theorem~\ref{thm:pres-norm} by induction on $e$:\\

  \noindent\textbf{Case} $\userule{N-Done}$ \\
  \indent Given that
  $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
  $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
  Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
  $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.\\

  \noindent\textbf{Case}\\
  $\userule{N-Repeat}$ \\
  \indent Given that
  $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
  $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
  Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
  $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$. Then by the
  induction hypothesis, we finally obtain that
  $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Sigma\infers s'''$.\\

@@

  We prove Theorem~\ref{thm:failing} by induction on $e'$.\\

@@

  % \noindent\textbf{Case} $e = u \At t$\\
  %  This case follows directly from applying the induction hypothesis, since $\Failing(u \At t,s)=\Failing(t,s)$ and any input that applies to $t$ also applies to $u \At t$.\\
\end{proof}

@@

  \case{$e=t_1\Or t_2 , i=\Second i$}
       {Given that $\userule{H-FirstOr}$ we have by definition that $\Inputs(t_1\Or t_2,s) = \set{\First\ i \mid i \in \Inputs(t_1,s)} \cup \set{\Second\ i \mid i \in \Inputs(t_2,s)}$.
       By the induction hypothesis, we have that $i\in\Inputs(t_2,s)$, and by definition of $\Inputs$, $\Second i$ is therefore als included in this case.}
  %
  % \noindent\textbf{Case} $e=u\At t, i$\\
  %  Given that $\userule{H-Appoint}$, we can directly apply the induction hypothesis to prove this case.\\
\end{proof}

>>>>

\begin{proof}
  We prove Theorem~\ref{thm:pres-eval} by induction on $e$:

@@

\begin{proof}
  We prove Lemma~\ref{lem:presvalue} by induction over $e$.

@@

  % \noindent\textbf{Case} $\Value{(u\At t,s)}=\Value(t,s)$ This case follows
  % directly from the induction hypothesis.
\end{proof}

@@

\begin{proof}
  We prove Theorem~\ref{thm:pres-stride} by induction on $e$:

@@

  \case{$\userule{S-ThenCont}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By Lemma~\ref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By Theorem~\ref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.}
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.

@@

\begin{proof}
  We prove Theorem~\ref{thm:pres-norm} by induction on $e$:

  \case{$\userule{N-Done}$}
    {Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
    $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
    $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.}

  \case
    {$\userule{N-Repeat}$}
    { Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
    $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
    $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$. Then by the
    induction hypothesis, we finally obtain that
    $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Sigma\infers s'''$.}

@@

  We prove Theorem~\ref{thm:failing} by induction on $e'$.

@@

  % \noindent\textbf{Case} $e = u \At t$
  %  This case follows directly from applying the induction hypothesis, since $\Failing(u \At t,s)=\Failing(t,s)$ and any input that applies to $t$ also applies to $u \At t$.
\end{proof}

@@

  \case{$e=t_1\Or t_2 , i=\Second i$}
       {Given that $\userule{H-FirstOr}$ we have by definition that $\Inputs(t_1\Or t_2,s) = \set{\First\ i \mid i \in \Inputs(t_1,s)} \cup \set{\Second\ i \mid i \in \Inputs(t_2,s)}$.
       By the induction hypothesis, we have that $i\in\Inputs(t_2,s)$, and by definition of $\Inputs$, $\Second i$ is therefore als included in this case.}
  %
  % \noindent\textbf{Case} $e=u\At t, i$
  %  Given that $\userule{H-Appoint}$, we can directly apply the induction hypothesis to prove this case.
\end{proof}
